\documentclass[12pt]{amsart}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{times}
\usepackage{amscd}
\usepackage[latin1]{inputenc}
\begin{document}
\begin{center}
{\bf \large On the complete integrability of the geodesic flow on pseudo-H type Lie groups}
\vspace{3ex}\\
Wolfram Bauer
\vspace{2ex}\\
{Leibniz Universität Hannover \vspace{1ex} \\
30167 Hannover, Germany \vspace{1ex}\\\
{bauer@math.uni-hannover.de}}
\vspace{4ex}
\end{center}
Pseudo-$H$ type groups form a subclass of all 2-step nilpotent Lie groups. They generalize the notion of Heisenberg and $H$-type groups and were introduced by P. Ciatti in 2000. 
More recently, the classification problem for such groups and the question whether they admit integral lattices have gained attention (see [2,3]). In a natural way such groups can 
be equipped with a left-invariant (pseudo)-Riemannian metric. 

In this talk we discuss the problem of complete integrability of the geodesic flow on pseudo-$H$ type groups. There are several sources for the explicit construction of sets of 
Poisson commuting first integrals. In particular, we explain how to obtain a maximal set which then proves the complete integrability. We mention that 
in the case of the Heisenberg group this problem has been previously solved in [4]. The problem of how to descend the first integrals to the quotient of the group by a standard lattice constructed in [3] is 
discussed. Finally, we address the question whether {\it "one can hear the complete integrability 
of the geodesic flow"}. More precisely, we ask whether the complete integrability of the geodesic flow of a closed Riemannian manifold is determined by the spectral data. In this framework 
two examples (not of pseudo-$H$-type) by D. Schueth are presented. 
\vspace{1mm}
\par
This talk is based on the joint work [1] with Daisuke Tarama (Ritsumeikan University, Japan). \vspace{1mm}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\sc References} 
\end{center}
{\small 
\begin{itemize}
\item[{[1]}] W. Bauer, D. Tarama, 
{\it On the complete integrability of the geodesic flow of pseudo-$H$-type Lie groups}, 
to appear in: {\it Analysis and Math. Phys}. 
\item[{[2]}] K. Furutani, I. Markina, 
{\it Complete classification of pseudo $H$-type Lie algebras: I}, 
Geom. Dedicata 190 (2017), 23 - 51. 
\item[{[3]}] K. Furutani, I. Markina, 
{\it Existence of lattice on general $H$-type groups}, 
J. Lie Theory 24, 979 - 1011. 
\item[{[4]}] A. Kocsard, G.P. Ovando, S. Reggiani, 
{\it The geodesic flow on nilmanifolds}, Differential Geom. Appl. 49 (2016), 496 - 509. 
\end{itemize}
}
\end{document}